In Section~\ref{sec:fixed} we present an exact, efficient algorithm for the
problem when the set of drivers and passengers is given in advanced.
In Section~\ref{sec:uwcm} we present a 2-approximation local search algorithm
for the unweighted variant of the problem.
In section~\ref{sec:cm} we give a 3-approximation algorithm for the problem.

In Section~\ref{sec:sub} we show that \carpool
can be formulated as an unconstrained submodular maximization problem,
thus it has a $\frac{1}{2}$-approximation algorithm due
to~\cite{BFNS15,buchbinder2016deterministic}.
%
We present a local search algorithm for \carpool which repeatedly
checks whether the current carpool matching can be improved by means
of a star centered at a vertex, and it terminates when such a step is
not possible.
%
The approximation ratio of this algorithm is $\half$ if weights are
polynomially bounded, and its ratio is $\half-\eps$ in general.

In Section~\ref{sec:cmax} we consider \carpool with boun\-ded maximum
capacity.   
%
In Section~\ref{sec:hardness} we show that \carpool is APX-hard even
for undirected and unweighted instances with $\Delta \leq b$, for any
$b \geq 3$.
%
In Section~\ref{sec:local} we provide another local search algorithm,
whose approximation ratio is $\half + \inv{2\cmax} - \eps$, for any
$\eps>0$, for unweighted \carpool, where $\cmax \eqdf \max_{v \in V}
c(v)$.  Given a parameter $k$, our algorithm starts with the empty
carpool matching.  Then, it repeatedly tries to find a better matching
by replacing $t \leq k$ arcs in the current solution by $t+1$ arcs
that are not in the solution.
%
We show that our analysis is tight.
%
We also note that our algorithm falls within the local search family
defined in~\cite{ACKK09}.  However, on undirected and uncapacitated
instances we have that $\cmax = \Delta$, and as mentioned above the
result from~\cite{ACKK09} does not hold in bounded degree graphs.

Finally, Section~\ref{sec:group} discusses \gcp.  We show that the
unconstrained submodular maximization formulation for \carpool does
not work for \gcp.  We show, however, that this problem still admits a
$(\frac{1}{2} -\varepsilon)$-approximation algorithm by extending our
first local search algorithm.  In addition, we show that the second
local search algorithm generalizes to unweighted \gcp with the same
approximation ratio.
